Incentivizing Exploration with Unbiased History

### 2018-11-01 llevel-overview.tex
O ---> O_K

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret. In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can achieve nearly optimal regret $O(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$. In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O(T^{1/2} polylog(T))$. 
\end{theorem}

@@

\begin{theorem}
\label{thm:llevel-2}
 We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta$ is the difference between the largest mean and second largest mean of arms. The recommendation policy does not depend on $\Delta$. Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{theorem}

>>>>

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret. In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can achieve nearly optimal regret $O_K(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O_K\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$. In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O_K(T^{1/2} polylog(T))$. 
\end{theorem}

@@

\begin{theorem}
\label{thm:llevel-2}
 We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O_K(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta$ is the difference between the largest mean and second largest mean of arms. The recommendation policy does not depend on $\Delta$. Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{theorem}
